---
title: "MSDS6306HW5_ANELSON"
author: "ANelson"
date: "October 9, 2017"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
getwd()
list.files()

```

## HW 5 QUestion 1a)
## Import y0b2016.txt into R; assign the dataframe to an object, df, that contains three human readable golumn names read.
```{r Q1a}
df <- read.table("yob2016.txt",sep=";",allowEscapes=F)
colnames(df) <- c("names","gender","n")
```

#Question 1b) display the summary and structure of df
```{r Q1b}
str(df)
summary(df)

```
#Question 1c) find the misspelled name
```{r Q1c}
test <- grep("yyy+", df$name)
badname <- df$name[test]
badname
```

#Question 1c) find the misspelled name
```{r Q1d}
y2016 <- df[!df$name[] == grep("yyy+", df$name),]
str(y2016)
```

## HW 5 QUestion 2a)
## Import yob2015.txt into R; assign the dataframe to an object, df, that contains three human readable golumn names read.
```{r Q2a}
y2015 <- read.csv("yob2015.txt", header=FALSE)
colnames(y2015) <- c("names","gender","n")
str(y2015)
```
#Question 2b) display the last ten rows of y2015 & describe something you find interesting about the last 10 rows
```{r Q2b}
tail(y2016,10)
#the last 10 rows all are male names with the same frequency...5
```
#Question 2c) merge y2016 & y2015 by the name column
```{r Q2c}
colnames(y2015) <- c("names","gender","n2015")
colnames(y2016) <- c("names","gender","n2016")
final <- na.omit(merge(y2016,y2015,by ="names"))
str(final)
```
#Question 3a) Create a new column total in dateframe final (sum of n2015 and n2016), how many people total were given popular names
### I am defining popular as names with > 30,000 occurances in 2015 + 2016

```{r Q3a}  
final$total <- final$n2016 + final$n2015
head(final)
biggest <- final[(final$total > 30000),]
str(biggest)
sum(biggest$total)

#Answer:  THere were 10 names with a total of 343,748 occurances. 
```

#Question 3c) 10 most popular girl names

```{r Q3c}
female <- final[(final$gender.x == "F" & final$gender.y == "F"),]
head(female[ with (female,order(-total)),],10)

```
#Question 3d) Write the 10 most popular girl names and Totals to a csv file

```{r Q3d}
top10girls <- head(female[ with (female,order(-total)),],10)

top10girls
top10girls$gender<- NULL
top10girls$gender.x <- NULL
top10girls$gender.y <- NULL
top10girls$n2015 <- NULL
top10girls$n2016 <- NULL
write.table(top10girls,file="girls.txt",row.names = F, sep = ",", col.names = F, quote=F)
#test that the write worked
testgirls <- read.csv("girls.txt")
testgirls


```
# link to gethub repository
##https://github.com/an1591/SMUHomework

```


```
